Numerical simulation and entropy dissipative cure of the carbuncle instability for the shallow water circular hydraulic jump

### 2021-08-09 numerics_paper/version2/numerical_chj.tex
add one of the missing experiments

>>>>

{\color{red}
  Finally, following \cite[Section III B]{kitamura2009evaluation}, we repeat the same experiment using
  the blended solver with an initial condition where the shock,
  located at $r_s=0.3$, is aligned with a grid interface. Afterward, we perturb the initial condition near the shock to misalign it
  from the grid interface. We use a mesh with $90$ elements in the radial direction and $90$ elements in the angular direction;
  see Figure \ref{fig:mesh_chj}.
  For this mesh, $\Delta r=(r_\out-r_\jet)/90=0.01$. 
  Let $(x_i,y_i)$ denote the coordinates of the center of the $i$-th element and $r_i:=\sqrt{x_i^2+y_i^2}$.
  For all elements where $r_i\not\in[r_s,r_s+\Delta r]$, we set
  \begin{align*}
    h_i = \frac{1}{\Delta r}\int_{r_i-\Delta r/2}^{r_i+\Delta r/2}h(r) dr,
    \qquad
    u_i = \frac{\beta}{h_ir_i}\left(\frac{x_i}{r_i}\right),
    \qquad
    v_i = \frac{\beta}{h_ir_i}\left(\frac{y_i}{r_i}\right),
  \end{align*}
  where $\beta=r_\jet h_\jet |u_\jet|$ and $h(r)$ is the solution of the ODE \eqref{steady} from either
  $r=r_\jet$ to $r=r_s^-$ or $r_s^+$ to $r_\out$.
  If $r_i = r_s+\Delta r/2$, we set
  \begin{align*}
    h_i = \delta h_L + (1+\delta) h_R,
    \qquad
    u_i = \frac{\beta}{h_ir_i}\left(\frac{x_i}{r_i}\right),
    \qquad
    v_i = \frac{\beta}{h_ir_i}\left(\frac{y_i}{r_i}\right),
  \end{align*}
  where $\delta=\{0,0.1,0.2,\dots,0.9,1\}$ and $h_L$ and $h_R$ are the values of the water height
  at the left and right cells from the cell with $r_i=r_s+\Delta r/2$, respectively.
  In Figure \ref{stab_shock_init_cond}, we plot $h(r,\theta_j)$ with $j=\{1,2,\dots,90\}$; that is,
  we plot the water height as a function of $r$ for every value of $\theta$.
  In Figures \ref{stab_shock_roe} and \ref{stab_shock_blended}, we plot the corresponding solutions at
  $t=3$ using method \eqref{second-order_via_fluct} with the Roe solver and with the blended solver,
  respectively. With the Roe solver, the carbuncle instability appears; as a consequence, the
  location of the shock changes for the different values of $\theta$.
  With the blended solver, no carbuncle instability appears and, therefore, all slices are aligned.
  In the figures we only show the results using $\delta=\{0,0.5,1\}$ but we
  obtained similar results with the other values of $\delta$.

  \begin{figure}
    \subfloat[Initial condition.\label{stab_shock_init_cond}]{
    \begin{tabular}{c}
      \includegraphics[scale=0.27,valign=c]{figures/chj_slices_delta0p0.png} \\ \\
      \includegraphics[scale=0.27,valign=c]{figures/chj_slices_delta0p5.png} \\ \\
      \includegraphics[scale=0.27,valign=c]{figures/chj_slices_delta1p0.png} 
    \end{tabular}
    }
    ~
    \subfloat[Roe's solver.\label{stab_shock_roe}]{
    \begin{tabular}{c}
      \includegraphics[scale=0.27,valign=c]{figures/chj_slices_delta0p0_roe.png} \\ \\
      \includegraphics[scale=0.27,valign=c]{figures/chj_slices_delta0p5_roe.png} \\ \\
      \includegraphics[scale=0.27,valign=c]{figures/chj_slices_delta1p0_roe.png} 
    \end{tabular}
    }
    ~
    \subfloat[Blended solver.\label{stab_shock_blended}]{
    \begin{tabular}{c}
      \includegraphics[scale=0.27,valign=c]{figures/chj_slices_delta0p0_blended.png} \\ \\
      \includegraphics[scale=0.27,valign=c]{figures/chj_slices_delta0p5_blended.png} \\ \\
      \includegraphics[scale=0.27,valign=c]{figures/chj_slices_delta1p0_blended.png} 
    \end{tabular}
  }    
    \caption{Simulation of a CHJ with boundary conditions given by \eqref{bcs_chj} and \eqref{bcs_chj_r1}.    
      We consider method \eqref{second-order_via_fluct} with different Riemann solvers.
      In (a) we show the different initial conditions that we consider.
      In (b) and (c) we show the corresponding solutions at $t=3$ using method
      \eqref{second-order_via_fluct} with the Roe solver and with the blended solver, respectively. 
      \label{fig:stab_shock}}
  \end{figure}
}
